---
title: "Measuring Efficiency on Milk Production Farms on the Cities of the Agreste Region of Pernambuco"
author: "Vitor Ferreira Lins"
date: "09 de dezembro de 2021"
output: 
   powerpoint_presentation:
      reference_doc: "style/style.pptx"
---

```{r setup, include=FALSE}
# Encoding: UTF-8
library(tmap)
library(tidyverse)
library(Benchmarking)
library(knitr)
library(readxl)
opts_chunk$set(echo = T)

# loading database, models and functions
load('data/environment.RData')
# loading personal ggplot2 styles
source('style/my_ggtheme.R')
```
# 1. Introduction

## 1.1. Objective

This study intends to conduct a efficiency analysis on the cow milk production in the cities of the Agreste region of the state of Pernambuco, in Brazil.

- Efficiency frontier
- Efficiency scores
- Improvement points
- Geographical clustering of the industry

# 2. Data

## 2.1. Discriptive statistics

```{r, echo=F}
var_names <- names(data[, -c(1:4)])
fqrt <- function(x) { quantile(x, prob =.25) }
tqrt <- function(x) { quantile(x, prob =.75) }
temp <- tibble(
  Variables =var_names,
  Mean =sapply(data[,var_names], mean),
  SD =sapply(data[,var_names], sd),
  `1st Quartile` =sapply(data[,var_names], fqrt),
  Median =sapply(data[,var_names], median),
  `3rd Quartile` =sapply(data[,var_names], tqrt)
)
kable(temp, digits =2, caption ="Source: IBGE, own elaboration")
rm(fqrt, tqrt, temp, var_names)
```

## 2.2. Biggest and smallest producers

:::::::::::::: {.columns}
::: {.column}

```{r echo=F}
l_milk_total <- sum(data$l_prod_milk)
data[order(data$l_prod_milk, decreasing =T), c("city", "l_prod_milk")] %>%
  mutate(percent ={(.$l_prod_milk/l_milk_total) *100}) %>%
  mutate(percent =paste0(round(percent,2), "%")) %>%
  setNames(c("City", "Milk Produced (liters)", "Total milk production")) %>%
  mutate(`Milk Produced (liters)` =as.character(`Milk Produced (liters)`)) -> temp
   rbind(
     temp[1:6,],
     tibble(
       City ="...",
       `Milk Produced (liters)` ="...", 
       `Total milk production` ="..."
      ),
     temp[64:70,]
    ) %>% kable(caption ="Source: IBGE, own elaboration.")
   
rm(l_milk_total, temp)

```

:::
::: {.column}

```{r echo=F}
tm_shape(data_wMap) + tm_polygons("l_prod_milk", palette ="Blues") +
  tm_text('city', remove.overlap =T)
```

:::
::::::::::::::

# 3. Model

## 3.1. Estimating possible models

```{r echo=F, fig.width=12}
plot_models()
```

## 3.2. Choosing a model

:::::::::::::: {.columns}
::: {.column}
### Credits and methodology:

- Before choosing a model, statistical tests performed with Wilson, Paul W. (2008)'s FEAR pakcage developed for R.
- And models were estimated with Peter Bogetoft and Lars Otto's Benchmarking package developed for R.
- The possible models contemplated (FDH and VRS) were chosen from the tests obtained for Convexity of the production and return to scale, respectively.
- The tests rejected both the **Convexity** hypothesis and **Constant Return to Scale**, so the models tested will follow at least one of the opposing assumptions.
:::
::: {.column}
### Models:

1. Free Disposability Hull (FDH) with fixed number of settlements and oriented for input and output;
2. Same as model 1, but only oriented for input;
3. Variable Return to Scale (VRS) with fixed number of settlements and oriented for input and output;
4. Same as model 3, but only oriented for input.
:::
::::::::::::::

## 3.3. Efficiency scores

``` {r fig.width=12, echo=F, fig.height =7}
plot_effs()
```

# 4. Bootstraping and Separability

## 4.1. Bootstraping results for the biggest and smallest productions
```{r fig.width=12, echo=F, fig.height =7}
slc <- order(data$l_prod_milk, decreasing =T)[c(1:6, 65:70)]

tibble(
  inf =results$bstrap_default$conf.int[,1],
  sup =results$bstrap_default$conf.int[,2]
) %>% mutate(
  dhat =results$bstrap_default$dhat.bc,
  bmp ={data$l_prod_milk >200},
  city =data$city
) -> temp

ggplot(temp[slc,], aes(x =city, color =bmp)) + 
  geom_point(aes(y ={1/dhat}), size =4) +
  geom_errorbar(ymin ={1/temp$inf[slc]}, ymax ={1/temp$sup[slc]}, size =1.2) +
  labs(x ='', y ='Estimated efficiency scores', color = 'Big milk producer') +
  expand_limits(y =c(0.25,1)) + custom_theme()
```

## 4.2. Separabily results

:::::::::::::: {.columns}
::: {.column}
- The separability tests included geographical placement of the cities, and the results generally reject the hypothesis of **Geogrphic impact** over the efficiency of the cities;
- The results are shown at the right side:
:::
::: {.column}
1. P-values with Latitude and Longitude:
**0.252, 0.509**;
2. P-values with Longitude only:
**0.029, 0.076**;
3. P-values with Latitude only:
**0.139, 0.123**.
:::
::::::::::::::
